---
title: "Classwork Activity"
author: "Hugo Andres Ramirez Tovar"
output: html_notebook
---


# Instructions (Step by Step)

## Step 1: Create fake data
```{r}
# Creating a small fake dataset
set.seed(2073) # allows for reproducibility 

students <- data.frame(
  Name = paste("Student", 1:20),
  StudyHours = round(runif(20, 1, 10), 1),
  Satisfaction = round(rnorm(20, mean = 7, sd = 1.5), 1),
  Major = sample(c("Data Science", "Business Analytics", "Math", "Computer Science"), 20, replace = TRUE)
)

head(students)
```


## Step 2: Drop a column

```{r}
# Remove the Name column

```


### Question:
Why might someone drop a column like name or ID from a dataset?

### Answer: Someone may drop a column like name or ID because the data is irrelevant or it may be redudant for the purpose of the dataset

## Step 3: Visualize
```{r}
library(ggplot2)
```

```{r}
ggplot(Students_Clean, aes(x = Major, y = Satisfaction, fill = Major)) +
  geom_boxplot() +
  labs(
    title = "Student Satisfaction by Major",
    x = "Major",
    y = "Satisfaction (1–10)"
  ) +
  theme_minimal()
```


## Step 4: Explain: Write 2–3 sentences each

### Questions:

1. What pattern or difference do you see in the chart?
2. What might explain it?
3. Do you think this chart is accurate?
4. Why? Why not?

### Answer:

1. A pattern I see in the chart is that students staisfaction on math is the highest one, but a difference I notice is that in the table, the satisfaction level is 9.3, while in the graph is below 8
2. One of the reasons could be that the values assigned to the chart are not as specific as the values appearing on the dataset, which led to a more ambigue result 
3. The data at the chart is not accurate compared to the data in the dataset
4. Because the diferenece bewtween the shown values in the graph and the dataset values are considerable

## Step 5: Questions on Git, GitHub and R Markdown

### Questions:

1. What does git add do?
2. What is the difference between git commit and git push?
3. Why is it useful to use GitHub for your code or data projects?
4. How could version control help when collaborating?
5. What is the difference between a code chunk and regular text in R Markdown?
6. How could R Markdown help you explain your analysis to someone else?

### Answers:

1. The function of Git add is to preparing the changes you have made for the next commit
2. Git commit record the changes in the repository, while Git push is used to interact with remote repositories
3. GitHub is useful for code data projects because  it allows to keep track of changes
4. version control helps keep track changes in collaborative projects
5. a code chunks is the one that allows you to run th code you have made, while  regular text is the text you want to add a

